Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-23 Paper/Paper.tex
improved

Finally, more related to our particular data, we try to assess how many
sustained patterns are represented in the codebook. We look at
the average variance over time, and we get an estimate of $60\%$ of the
codebook (Figure \ref{fig:code_var}).  25\% of the codebook correspond
to very simple sustained patterns similar to the top row of Figure
\ref{fig:codes1}.  How is this different from the next 35\%?

>>>>

Finally, more related to our particular data, we try to assess how many
sustained patterns are represented in the codebook. We look at
the average variance over time in Figure \ref{fig:code_var}.
25\% of the codebook correspond
to very simple sustained patterns similar to the top row of Figure
\ref{fig:codes1}. For $2$ bars codewords, it seems that interesting
patterns appear in only $33$\% of the data.
